\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: Revision of Section 4.3

In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following work by \citet{saffman_1986}. In this manuscript, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem mathematical formulation and solutions.

>>>>

In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following the work by \citet{saffman_1986}. In this manuscript, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem's mathematical formulation and solutions.
